---
title: ""
output: html_document
---
  
 
```{r , echo=FALSE, include = FALSE}
library(rvest)
library(tidyverse)
library(stringi)
library(readxl)
library(janitor)
library(DT)
library(xml2)
library(lubridate) 
library(RSelenium)
library(httr2)

# https://vikyd.github.io/download-chromium-history-version/#/
# https://commondatastorage.googleapis.com/chromium-browser-snapshots/index.html?prefix=Win/1047731/


# download crome-win-zip, unpack, execute
#binman::list_versions("chromedriver")
# library(wdman)
# chromecommand<-chrome(retcommand = T, verbsoe = F, check = F)
# chromecommand
#C:\Users\Jochen\AppData\Local\binman\binman_chromedriver\win32
#https://www.youtube.com/watch?v=BnY4PZyL9cg

#https://chromedriver.chromium.org/downloads
# get latest for windowns 64
# this folder; C:\Users\Jochen\AppData\Local\binman\binman_chromedriver\win32
# Rename folder with current chrome version (not chromedriver version)
# replace also number here (chrome version, not chromedriver version number)

date1 <- today()-7
date2 <- today()


get_ssrn <- function(index) {
  cat("Scraping index:", index, "\n")
  str_c("https://api.ssrn.com/content/v1/bindings/204/papers?index=", 
        index, "&count=200&sort=0") %>%
    request() %>%
    req_perform() %>%
    resp_body_json(simplifyVector = TRUE) %>%
    pluck("papers") %>%
    as_tibble() 
}

df <- map_dfr(seq(0, 200, by = 200), get_ssrn)


ssrn <- as.data.frame(df) %>% 
  mutate(
    title = title,
    authors = authors,
    info = reference,
    affiliation = affiliations,
    date = approved_date,
    url2 = url
         ) %>% 
  unnest() %>% 
  mutate(authors = paste0(first_name," ",last_name)) %>% 
  select(title, authors, affiliation, info, date, url2) %>% 
  group_by(title) %>% 
  mutate(authors = paste0(authors, collapse = "; ")) %>% ungroup() %>% 
  group_by(url2) %>% 
  filter(row_number() == 1) %>% ungroup() %>% 
  separate(date,into=c("day","mon","year"),sep = " ") %>% 
  mutate(mon = match(mon,month.abb)) %>% 
  mutate(date = paste(year, mon, day,sep="-")) %>% 
  mutate(date = as.Date(date)) %>% 
  select(-year,-mon,-day)  


# Combine
data_ssrn_acc <- ssrn %>% filter(date >= date1) %>% filter(date <= date2)    %>% 
  mutate(title = paste0("<a href='",url2,"' target='_blank'>",title,"</a>")) %>% 
  select(-url2) %>% 
  select(-date)



# Tandfonline Journals
journal_codes <- c("rabr20", "rear20", "racc20", "raie20")
tandfonline = data.frame() 
for(c in journal_codes) {

rD <- rsDriver(
  browser = "chrome",
  chromever = "123.0.6312.58", # ***IMPORTANT: check local chrome version***
  verbose = FALSE,
)
remDr <- rD[["client"]]  
    
url <- paste0("https://www.tandfonline.com/action/showAxaArticles?journalCode=",c) 

remDr$navigate(url)
  Sys.sleep(5)
  html <- remDr$getPageSource()[[1]]

webpage <- read_html(html)
title <- webpage %>% 
  html_nodes("div.art_title.linkable") %>% 
  html_text()  %>%
  data.frame()
colnames(title)[1] <- "title"
authors <- webpage %>% 
  html_nodes("div.tocAuthors.articleEntryAuthor") %>% 
  html_text()  %>%
  data.frame()
colnames(authors)[1] <- "authors"  
link <- webpage %>% 
  html_nodes("a.ref.nowrap") %>% 
  xml_attr("href") %>%
  data.frame()
colnames(link)[1] <- "link"
link <- link %>% mutate(link = paste0("https://www.tandfonline.com",link))
date <- webpage %>% 
  html_nodes("div.tocEPubDate") %>% 
  html_text()  %>%
  data.frame()
colnames(date)[1] <- "date"
date <- date %>%   separate(date,into=c("text","date"),sep = "Published online:") %>%  select(date) 
 data <- cbind(title, link, date) %>% 
  mutate(source = c) %>%
  mutate(source = ifelse(source == "rabr20","ABR",source),
         source = ifelse(source == "rear20","EAR",source),
         source = ifelse(source == "racc20","AF",source),
         source = ifelse(source == "raie20","AiE",source)
         ) %>% 
  mutate(date = gsub(" ", "", date)) %>% 
  mutate(date = as.Date(date,"%d%b%Y")) %>%  
  filter(title != "Correction") 
data <- cbind(data,authors) 
tandfonline = rbind(tandfonline , data)
 remDr$close()
 rD[["server"]]$stop()
  system("taskkill /im java.exe /f", intern=FALSE, ignore.stdout=FALSE)

}
EAR <- tandfonline %>% filter(source == "EAR")
ABR <- tandfonline %>% filter(source == "ABR")
AF <- tandfonline %>%  filter(source == "AF")
AiE <- tandfonline %>%  filter(source == "AiE")

# Elsevier journals 
journal_codes <- c("journal-of-accounting-and-economics","journal-of-accounting-and-public-policy","management-accounting-research","critical-perspectives-on-accounting","accounting-organizations-and-society")


elsevier = data.frame() 
for(c in journal_codes) {
  
rD <- rsDriver(
  browser = "chrome",
  chromever = "123.0.6312.58", # ***IMPORTANT: check local chrome version***
  verbose = FALSE,
)
 
 
remDr <- rD[["client"]]  
    
url <- paste0("https://www.sciencedirect.com/journal/",c,"/articles-in-press") 

remDr$navigate(url)
  Sys.sleep(15)
  html <- remDr$getPageSource()[[1]] 
  
webpage <- read_html(html)  
title <- webpage %>% 
  html_nodes("span.js-article-title") %>% 
  html_text("title")  %>%
  data.frame()
colnames(title)[1] <- "title"
authors <- webpage %>% 
  html_nodes("div.text-s.u-clr-grey8.js-article__item__authors") %>% 
  html_text()  %>%
  data.frame()
colnames(authors)[1] <- "authors"
link <- webpage %>% 
  html_nodes("a.anchor.article-content-title.u-margin-xs-top.u-margin-s-bottom") %>% 
  xml_attr("href")  %>%
  data.frame()
colnames(link)[1] <- "link"
link <- link %>% mutate(link = paste0("https://www.sciencedirect.com/",link))
date <- webpage %>% 
  html_nodes("span.u-clr-grey8.u-text-italic.text-s.js-article-item-aip-date") %>% 
  html_text()  %>%
  data.frame()
colnames(date)[1] <- "date"
date <- date %>%   separate(date,into=c("text","date"),sep = "Available online") %>%  select(date) 
data <- cbind(title, link, date) %>% 
  filter(title != "Acknowledgements") %>% 
  filter(title != "Acknowledgement") %>%  
  filter(title != "Call for Papers") %>%  
  filter(title != "Call for paper") %>% 
  filter(title != "Call for papers") %>% 
  filter(title != "BIO") %>% 
  filter(title != "Bio") %>% 
  mutate(
         drop=(ifelse(str_detect(title,"Prize Announcement"),1,0)),
         drop=(ifelse(str_detect(title,"ANNOUNCEMENT"),1,drop)), 
         drop=(ifelse(str_detect(title,"Announcement:"),1,drop)),
          drop=(ifelse(str_detect(title,"Call for papers"),1,drop)),
         drop=(ifelse(str_detect(title,"Biographies"),1,drop)),   
         drop=(ifelse(str_detect(title,"Bios"),1,drop)),   
         drop=(ifelse(str_detect(title,"BIOGRAPHIES"),1,drop)), 
         drop=(ifelse(str_detect(link,"S1044500519300113"),1,drop)),
         drop=(ifelse(str_detect(link,"S1044500520300184"),1,drop)), 
         drop=(ifelse(str_detect(title,"ublisher"),1,drop))
         )  %>% 
  filter(drop == 0) %>% select(-drop)
authors <- authors %>% 
  mutate(drop=(ifelse(str_detect(authors,"Wim A. Van der Stede"),1,0)))  %>% 
  filter(drop == 0) %>% select(-drop)
data <- cbind(data, authors) %>% 
    mutate(source = c) %>%
    mutate(source = ifelse(source == "journal-of-accounting-and-economics","JAE",source),
         source = ifelse(source == "journal-of-accounting-and-public-policy","JAPP",source),
         source = ifelse(source == "accounting-organizations-and-society","AOS",source),
         source = ifelse(source == "management-accounting-research","MAR",source),
         source = ifelse(source == "critical-perspectives-on-accounting","CPA",source)
                            ) %>%
  mutate(date = gsub(" ", "", date)) %>% 
  mutate(date = as.Date(date,"%d%b%Y"))
elsevier = rbind(elsevier , data)
 remDr$close()
 rD[["server"]]$stop()
  system("taskkill /im java.exe /f", intern=FALSE, ignore.stdout=FALSE)
}
JAE <- elsevier %>% filter(source == "JAE")
JAPP <- elsevier %>% filter(source == "JAPP")
AOS <- elsevier %>% filter(source == "AOS")
MAR <- elsevier %>% filter(source == "MAR")
CPA <- elsevier %>% filter(source == "CPA")

# allenpress
journal_codes <- c("accounting-review", "jmar","accounting-horizons", "jata", "ajpt")
allenpress = data.frame() 
for(c in journal_codes) {
########### TAR
url <- paste0("https://meridian.allenpress.com/",c,"/publish-ahead-of-print")
webpage <- read_html(url)
title <- webpage %>% 
  html_nodes("h5.al-title") %>% 
  html_text()  %>%
  data.frame()
colnames(title)[1] <- "title"
authors <- webpage %>% 
  html_nodes("div.al-authors-list") %>% 
  html_text()  %>%
  data.frame()
colnames(authors)[1] <- "authors"  
link <- webpage %>% 
  html_nodes("h5.al-title") %>% html_nodes("a") %>% 
  xml_attr("href") %>%
  data.frame()
colnames(link)[1] <- "link"
link <- link %>% mutate(link = paste0("https://meridian.allenpress.com",link))
link <- link %>% filter(link != "https://meridian.allenpress.comhttp://aaajournals.org/doi/full/10.2308/accr-51520")
date <- webpage %>% 
  html_nodes("span.sri-date.al-pub-date") %>% 
  html_text()  %>%
  data.frame()
colnames(date)[1] <- "date"
data <- cbind(title, authors, link, date) %>% 
  mutate(source = c) %>%
  mutate(source = ifelse(source == "accounting-review","TAR",source),
         source = ifelse(source == "jmar","JMAR",source),
         source = ifelse(source == "accounting-horizons","AH",source),
         source = ifelse(source == "jata","JATA",source),
         source = ifelse(source == "ajpt","AJPT",source)
         ) %>% 
  mutate(title = sub("^\\s+", "", title)) %>% 
  mutate(authors = sub("^\\s+", "", authors)) %>% 
  separate(date,into=c("mon","day","year"),sep = " ") %>% 
  mutate(mon = match(mon,month.name)) %>% 
  mutate(date = paste(year, mon, day,sep="-")) %>% 
  mutate(date = as.Date(date)) %>% 
  select(-year,-mon,-day)  
allenpress = rbind(allenpress , data)
}
TAR <- allenpress %>% filter(source == "TAR")
JMAR <- allenpress %>% filter(source == "JMAR") 
AH <- allenpress %>% filter(source == "AH") 
JATA <- allenpress %>% filter(source == "JATA") 
AJPT <- allenpress %>% filter(source == "AJPT") 


# Wiley


rD <- rsDriver(
  browser = "chrome",
  chromever = "123.0.6312.58", # ***IMPORTANT: check local chrome version***
  verbose = FALSE,
)
remDr <- rD[["client"]]


journal_codes <- c("14685957")
# Checjk: SMJ 10970266
wiley = data.frame() 
for(c in journal_codes) {

url <- paste0("https://onlinelibrary.wiley.com/journal/",c,"?tabActivePane=")
  
remDr$navigate(url)
 Sys.sleep(15)
  html <- remDr$getPageSource()[[1]]
  
webpage <-  read_html(html) 
title <- webpage %>% 
  html_nodes("h3.issue-item__title.issue-item__title__en") %>% 
  html_text()  %>%
  data.frame()
colnames(title)[1] <- "title"
authors <- webpage %>% 
  html_nodes("div.loa.comma") %>% 
  html_text()  %>%
  data.frame()
colnames(authors)[1] <- "authors"
link <- webpage %>% 
  html_nodes("a.issue-item__title.visitable") %>% 
  xml_attr("href")  %>%
  data.frame()
colnames(link)[1] <- "link"
link <- link %>% mutate(link = paste0("https://onlinelibrary.wiley.com",link))
date <- webpage %>% 
  html_nodes("ul.rlist--inline.separator.issue-item__details") %>% 
  html_text()  %>%
  data.frame()
colnames(date)[1] <- "date"
date <- date %>%   separate(date,into=c("text","date"),sep = "First Published:") %>%  select(date) %>% 
  mutate(date = gsub("&nbsp", "", date)) 
data <- cbind(title, link, date) %>% 
    mutate(source = c) %>% 
    mutate(source = ifelse(source == "14685957","JBFA",source),
         source = ifelse(source == "19113846","CAR",source)
         ) %>% 
  mutate(date = sub("^\\s+", "", date)) %>% # delete leading space
  separate(date,into=c("day","mon","year"),sep = " ") %>% 
  mutate(mon = match(mon,month.name)) %>% 
  mutate(date = paste(year, mon, day,sep="-")) %>% 
  mutate(date = as.Date(date)) %>% 
  select(-year,-mon,-day)  %>% 
  mutate(drop=(ifelse(str_detect(title,"AMERICAN FINANCE ASSOCIATION"),1,0)),
           drop=(ifelse(str_detect(title,"AMERICAN FINANCE ASSOCIATION"),1,drop)),
         drop=(ifelse(str_detect(title,"Annual Membership"),1,drop)),
         drop=(ifelse(str_detect(title,"Jean Tirole"),1,drop)),
         drop=(ifelse(str_detect(title,"MISCELLANEA"),1,drop)),
         drop=(ifelse(str_detect(title,"James M. Poterba"),1,drop)),
         drop=(ifelse(str_detect(title,"ANNOUNCEMENT"),1,drop)),
         drop=(ifelse(str_detect(title,"Report of the Executive Secretary"),1,drop)),
         drop=(ifelse(str_detect(title,"ANNOUNCEMENTS"),1,drop)),
         drop=(ifelse(str_detect(title,"Corrigendum"),1,drop)),
         drop=(ifelse(str_detect(title,"Retracted"),1,drop)),
         drop=(ifelse(str_detect(title,"Ad Hoc Reviewers"),1,drop))
  ) %>% 
  filter(drop == 0) %>% select(-drop)
data <- cbind(data,authors)
 wiley = rbind(wiley , data)
 remDr$close()
 rD[["server"]]$stop()
  system("taskkill /im java.exe /f", intern=FALSE, ignore.stdout=FALSE)
}


#CAR
journal_codes <- c(  "19113846")
wiley2 = data.frame() 
for(c in journal_codes) {

rD <- rsDriver(
  browser = "chrome",
  chromever = "123.0.6312.58", # ***IMPORTANT: check local chrome version***
  verbose = FALSE,
)
remDr <- rD[["client"]]  
  
url <- paste0("https://onlinelibrary.wiley.com/journal/",c,"?tabActivePane=")

remDr$navigate(url)
  Sys.sleep(15)
  html <- remDr$getPageSource()[[1]]

webpage <- read_html(html)
title <- webpage %>% 
  html_nodes("h3.issue-item__title.issue-item__title__en") %>% 
  html_text()  %>%
  data.frame()
colnames(title)[1] <- "title"
authors <- webpage %>% 
  html_nodes("div.loa.comma") %>% 
  html_text()  %>%
  data.frame()
colnames(authors)[1] <- "authors"
link <- webpage %>% 
  html_nodes("a.issue-item__title.visitable") %>% 
  xml_attr("href")  %>%
  data.frame()
colnames(link)[1] <- "link"
link <- link %>% mutate(link = paste0("https://onlinelibrary.wiley.com",link))
date <- webpage %>% 
  html_nodes("ul.rlist--inline.separator.issue-item__details") %>% 
  html_text()  %>%
  data.frame()
colnames(date)[1] <- "date"
date <- date %>%   separate(date,into=c("text","date"),sep = "First Published:") %>%  select(date) %>% 
  mutate(date = gsub("&nbsp", "", date)) 
data <- cbind(title, link, date) %>% 
    mutate(source = c) %>% 
    mutate(source = ifelse(source == "14685957","JBFA",source),
         source = ifelse(source == "19113846","CAR",source)
         ) %>% 
  mutate(date = sub("^\\s+", "", date)) %>% # delete leading space
  separate(date,into=c("day","mon","year"),sep = " ") %>% 
  mutate(mon = match(mon,month.name)) %>% 
  mutate(date = paste(year, mon, day,sep="-")) %>% 
  mutate(date = as.Date(date)) %>% 
  select(-year,-mon,-day)  %>% 
  mutate(drop=(ifelse(str_detect(title,"AMERICAN FINANCE ASSOCIATION"),1,0)),
         drop=(ifelse(str_detect(title,"Annual Membership"),1,drop)),
         drop=(ifelse(str_detect(title,"Jean Tirole"),1,drop)),
         drop=(ifelse(str_detect(title,"MISCELLANEA"),1,drop)),
         drop=(ifelse(str_detect(title,"James M. Poterba"),1,drop)),
         drop=(ifelse(str_detect(title,"ISSUE INFORMATION"),1,drop)),
         drop=(ifelse(str_detect(title,"Corrigendum"),1,drop)),
         drop=(ifelse(str_detect(title,"Retracted"),1,drop)),
         drop=(ifelse(str_detect(title,"AFA 2022"),1,drop)),
         drop=(ifelse(str_detect(title,"ANNOUNCEMENT"),1,drop)),
         drop=(ifelse(str_detect(title,"Corrections for Du"),1,drop)),
         drop=(ifelse(str_detect(title,"Ad Hoc Reviewer"),1,drop)),
         drop=(ifelse(str_detect(title,"Reviewer Recognition Program"),1,drop)),
         drop=(ifelse(str_detect(title,"Report of the Executive Secretary"),1,drop)),
         drop=(ifelse(str_detect(title,"ERRATUM"),1,drop)),
         drop=(ifelse(str_detect(title,"ANNOUNCEMENTS"),1,drop)),
         drop=(ifelse(str_detect(title,"Article Note/Editorial Note"),1,drop)),
         drop=(ifelse(str_detect(title,"Ad Hoc Reviewers"),1,drop))
  ) %>% 
  filter(drop == 0) %>% select(-drop)
data <- cbind(data,authors)
wiley2 = rbind(wiley2 , data)
 remDr$close()
 rD[["server"]]$stop()
  system("taskkill /im java.exe /f", intern=FALSE, ignore.stdout=FALSE)
}

wiley <- rbind(wiley2, wiley)

JBFA <- wiley %>% filter(source == "JBFA")
CAR <- wiley %>% filter(source == "CAR")


# jar only
rD <- rsDriver(
  browser = "chrome",
  chromever = "123.0.6312.58", # ***IMPORTANT: check local chrome version***
  verbose = FALSE,
)
remDr <- rD[["client"]]    
url <- paste0("https://onlinelibrary.wiley.com/journal/1475679x?tabActivePane=undefined")
remDr$navigate(url)
  Sys.sleep(15)
  html <- remDr$getPageSource()[[1]]
webpage <- read_html(html) 
title <- webpage %>% 
  html_nodes("h3.issue-item__title.issue-item__title__en") %>% 
  html_text()  %>%
  data.frame()
colnames(title)[1] <- "title"
authors <- webpage %>% 
  html_nodes("div.loa.comma") %>% 
  html_text()  %>%
  data.frame() %>% 
  filter(row_number()<=10)
colnames(authors)[1] <- "authors"
link <- webpage %>% 
  html_nodes("a.issue-item__title.visitable") %>% 
  xml_attr("href")  %>%
  data.frame()
colnames(link)[1] <- "link"
link <- link %>% mutate(link = paste0("https://onlinelibrary.wiley.com",link))
date <- webpage %>% 
  html_nodes("ul.rlist--inline.separator.issue-item__details") %>% 
  html_text()  %>%
  data.frame()
colnames(date)[1] <- "date"
date <- date %>%   separate(date,into=c("text","date"),sep = "First Published:") %>%  select(date) %>% 
  mutate(date = gsub("&nbsp", "", date)) 
data <- cbind(title, link, date) %>% 
  mutate(date = sub("^\\s+", "", date)) %>% # delete leading space
  separate(date,into=c("day","mon","year"),sep = " ") %>% 
  mutate(mon = match(mon,month.name)) %>% 
  mutate(date = paste(year, mon, day,sep="-")) %>% 
  mutate(date = as.Date(date)) %>% 
  select(-year,-mon,-day)  %>% 
  mutate(drop=(ifelse(str_detect(title,"Call for Papers"),1,0)),
         drop=(ifelse(str_detect(title,"Request for Papers"),1,drop)),
          drop=(ifelse(str_detect(title,"Excellence in Refereeing"),1,drop)),
         drop=(ifelse(str_detect(title,"Issue Information"),1,drop))) %>%
  filter(drop == 0) %>% select(-drop) %>%
  mutate(source="JAR") %>% 
  filter(row_number()<=10)
JAR <- cbind(data,authors) 
remDr$close()
 rD[["server"]]$stop()
  system("taskkill /im java.exe /f", intern=FALSE, ignore.stdout=FALSE)



# Srpinger
journal_codes <- c("11142")
springer = data.frame() 
for(c in journal_codes) {
  url <- paste0("https://www.springer.com/journal/",c)
  webpage <- read_html(url)
  title <- webpage %>% 
  html_nodes("article") %>% html_nodes("a") %>% 
  html_text()  %>%
  data.frame()
colnames(title)[1] <- "title"
authors <- webpage %>% 
  html_nodes("ul.c-author-list") %>% 
  html_text()  %>%
  data.frame()
colnames(authors)[1] <- "authors"
link <- webpage %>% 
  html_nodes("article") %>% html_nodes("a") %>% 
  xml_attr("href")  %>%
  data.frame()
colnames(link)[1] <- "link"
date <- webpage %>% 
  html_nodes("span.c-meta__item") %>% 
  html_text()  %>%
  data.frame()
colnames(date)[1] <- "date"
date <- date %>% 
    mutate(drop=(ifelse(str_detect(date,"Paper"),1,0)),
           drop=(ifelse(str_detect(date,"Open"),1,drop))) %>% 
  filter(drop == 0) %>% select(-drop) 
data <- qpcR:::cbind.na(title, authors, link, date) %>% 
  filter(!is.na(authors)) %>% 
  mutate(source = c) %>%
  mutate(source = ifelse(source == "11142","RAST",source)) %>% 
  mutate(date = sub("^\\s+", "", date)) %>%
  mutate(date = gsub("[[:space:]]*$","",date)) %>% 
  separate(date,into=c("day","mon","year"),sep = " ") %>% 
  mutate(mon = match(mon,month.name)) %>% 
  mutate(date = paste(year, mon, day,sep="-")) %>% 
  mutate(date = as.Date(date)) %>% 
  select(-year,-mon,-day)  
springer = rbind(springer , data)
}
RAST <- springer %>% filter(source == "RAST")


# AAAJ Reading the HTML code from the website
url <- paste0("https://www.emerald.com/insight/publication/issn/0951-3574#earlycite")
  webpage <- read_html(url)
title <- webpage %>% 
    html_nodes("h4.h4.mt-0.mb-2.font-serif") %>% 
    html_text()  %>%
    data.frame()
  colnames(title)[1] <- "title"
link <- webpage %>% 
    html_nodes("h4.h4.mt-0.mb-2.font-serif") %>%   html_nodes("a") %>%
    xml_attr("href") %>%
    data.frame()
  colnames(link)[1] <- "link"
  link <- link %>% mutate(link = paste0("https://www.emerald.com/",link))
AAAJ <- cbind(title, link) %>% 
    mutate(source = "AAAJ")

# Function --> webpage
scraper1<- function(url){
    webpage <- read_html(url) 
   date <- webpage %>% 
    html_nodes("span.intent_journal_publication_date") %>% 
    html_text()  %>%
    data.frame()
  colnames(date)[1] <- "date"
  date <- date %>%   separate(date,into=c("text","date"),sep = "publication date:") %>%  select(date) %>% 
    mutate(date = sub("^\\s+", "", date)) %>%
    separate(date,into=c("day","mon","year"),sep = " ") %>% 
    mutate(mon = match(mon,month.name)) %>% 
    mutate(date = paste(year, mon, day,sep="-")) %>% 
    mutate(date = as.Date(date)) %>% 
    select(-year,-mon,-day)  
  authors <- webpage %>% 
    html_nodes("a.contrib-search") %>% 
    html_text()  
  authors <- paste(authors[1],",",authors[2],",",authors[3],",",authors[4],",",authors[5],",",authors[6]) %>% data.frame() 
  colnames(authors)[1] <- "authors"
  authors <- authors %>% 
    mutate(authors = gsub(", NA", "", authors))
  table <- cbind(date,authors)
}
AAAJ <- AAAJ %>% 
  mutate(c = purrr::map(AAAJ$link, scraper1 )) %>% 
  unnest(col = c) 


published <- rbind(ABR, AF, AH, AJPT, AiE, AOS, CAR,  CPA, EAR, JAR, JAE, JAPP, JATA,  JBFA, JMAR,  MAR, RAST, TAR, AAAJ ) %>% 
    mutate(authors = sub("^\\s+", "", authors)) %>% 
  filter(date >= date1) %>% filter(date <= date2) %>% 
  mutate(title = paste0("<a href='",link,"' target='_blank'>",title,"</a>")) %>% 
 select(-link,-date ) 


  
text <- paste0("New publications (online first) from ",date1," to ",date2)
text3 <- paste0("New SSRN working papers (Accounting Research Network) from ",date1," to ",date2)






```



<br><br><br><br><br>  <br><br>

<head>
<meta name="twitter:card" content="summary_large_image">
<meta name="twitter:site" content="@@updates_acc">
<meta name="twitter:creator" content="@jochenpierk">
<meta name="twitter:title" content="New Publications">
<meta name="twitter:description" content="Weekly update of new publications and SSRN working papers.">
<meta name="twitter:image" content="http://easys-online.com/wp-content/uploads/2021/03/pic_twitter-2.jpg" >



<meta name="title" property="og:title" content="New Accounting Publications">
<meta name="description" property="og:description" content="Weekly update of new accounting publications and SSRN working papers! Feel free to sign up via email. Enjoy reading!">
<meta name="image" property="og:image" content="http://easys-online.com/wp-content/uploads/2021/03/pic_twitter-2.jpg">



</head>

<style>
  .nav-pills>li>a {
     color: black;
     padding-left: 200px;
     }
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     color: black;
     }
  .nav-pills > li:nth-of-type(2)>a {
     color: black;
      padding-left: 1px;
      text-align: center;
    }
  .nav-pills > li:nth-of-type(2)>a:hover, .nav-pills > li:nth-of-type(2)>a:focus, .nav-pills > li:nth-of-type(2).active>a {
     color: black;
    
     }
  .nav-pills > li:nth-of-type(3)>a {
     color: black;
      padding-left: 1px;

    }
  .nav-pills > li:nth-of-type(3)>a:hover, .nav-pills > li:nth-of-type(2)>a:focus, .nav-pills > li:nth-of-type(2).active>a {
     color: black;
    }
  </style>   
    
    
  <style type="text/css">
.main-container {
  max-width: 70% !important;
  margin: auto;
}
</style>  
     

<!-- Global site tag (gtag.js) - Google Analytics -->
<script async src="https://www.googletagmanager.com/gtag/js?id=G-ZGC80EMKSJ"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'G-ZGC80EMKSJ',{'anonymize_ip': true});
</script>

## Accounting Updates {.tabset .tabset-fade .tabset-pills }


For a weekly update via email, please sign up [here](https://jochenpierk.github.io/acc_update/subscribe.html). [Previous weeks](https://jochenpierk.github.io/home/service2/). [Unsubscribe](mailto:acco.updates@gmail.com?Subject=Please%20unsubscribe%20me&Body=Hi%20Jochen%20Please%20delete%20me%20from%20the%20list%20Thanks.). 

## New Publications   

```{r, echo = FALSE,  results = "asis"}

cat(text)

datatable(published,escape = FALSE,  list(pageLength = 50))

```
Journals included: Accounting Auditing & Accountability Journal (AAAJ), Accounting and Business Research (ABR), Accounting Forum (AF), Accounting in Europe (AiE), Auditing: A Journal of Practice & Theory  (AJPT), Accounting Organization and Society (AOS), Accounting Horizon (AH), Contemporary Accounting Research (CAR), Critical Perspectives on Accounting (CPA), European Accounting Review (EAR), Journal of Accounting and Economics (JAE), Journal of Accounting and Public Policy (JAPP), Journal of Accounting Research (JAR), Journal of the American Taxation Association (JATA), Journal of Business Finance and Accounting (JBFA),  Journal of Mangement Accounting Research (JMAR), Management Accounting Research (MAR), Review of Accounting Studies (RAST), and The Accounting Review (TAR).



## New SSRN Working Papers {.tabset .tabset-fade .tabset-pills}


```{r, echo = FALSE,  results = "asis"}

cat(text3)

datatable(data_ssrn_acc, escape = FALSE,  list(pageLength = 100))
```




